MacLeish: An R package for monitoring environmental conditions in Whately, Massachusetts

### 2025-11-21 README.Rmd
updated URL

The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.

@@

- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
- **[etl](https://github.com/beanumber/etl)**

>>>>

The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/discover-smith/smith-action/sustainable-smith/macleish-field-station) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.

@@

- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/discover-smith/smith-action/sustainable-smith/macleish-field-station)
- **[etl](https://github.com/beanumber/etl)**

### 2025-11-21 joss_paper/paper.Rmd
updated URL

From the [Smith College website]([Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)):

>>>>

From the [Smith College website]([Ada and Archibald MacLeish Field Station](https://www.smith.edu/discover-smith/smith-action/sustainable-smith/macleish-field-station)):
